\part{General Rules and Definitions \label{part:general}}
\parttoc
\thispagestyle{empty}

\chapter{General}

\section{Scope of Rules}

This rulebook is intended to govern NAUCC. All NAUCCs (North American Unicycle Convention and Championships) must abide exclusively by these rules.
Further rules may be added to cover specific situations, but they may not override the USA rules without prior approval by the USA Board of Directors.
All additional rules must be published well in advance of competition.

\section{How to Use This Rulebook}%usa2017

This chapter is meant to replace chapter 1 of the IUF Rulebook for the use at USA events.
The following chapters in the IUF Rulebook will be used, along with the USA Amendments, and these chapters in the IUF Rulebook are organized by discipline.
Each chapter includes a overview, competitor rules, officials rules, and organizer rules.
Additionally, Chapter 1 covers general rules, not tied to a particular event.

How you approach the information in this rulebook will depend on what role you play.
The information has been organized with a goal toward separating rules by role, so that you can safely ignore sections that do not pertain to you.
For example, if you are only interested in muni as a competitor, you can ignore other chapters and you can mostly ignore the officials and organizer rules within the muni chapter.

The following table gives some guidance for what information you need for various roles:

\begin{longtable}{|l|p{8cm}|}
\hline
\textbf{Role} & \textbf{Applicable Sections} \\
\hline
Competitor & Chapter 1 and the overview and competitor rules for your events\\
\hline
Official & Chapter 1 and the overview, competitor rules, and officials rules for the event you will officiate\\
\hline
Event director & Chapter 1 and all sections of the chapter for your event \\
\hline
Host & All sections of the rulebook\\
\hline
\end{longtable}

\section{How the Rulebook is Updated}
This publication should be updated every two years following the latest IUF Rulebook publication.
The Committee should finish their business and publicize the publication no less than four months before the start day of the next NAUCC.
This is meant to be the only time that changes to the Rulebook are made, although exceptions are possible in extraordinary cases.
The USA Board is responsible for making sure that the Rulebook Committee stays focused and on schedule.

Anyone may submit a potential change to the Rulebook at any time.
These will not be official proposals, but suggestions for potential topics during the next Rulebook session.
A forum can also be provided to discuss potential changes throughout the year.

\section{North American Champions}
The Male and Female winners of each individual event at NAUCC are the North American Champions for that event.
There is no age limit to winning the overall title.

Age group winners can use the title `Age-Group Winner', and the term `North American Champions' generally refers to winners of Overall, Finals or Expert class.

\section{World Records}

The host is strongly encouraged to ensure that the competitions are conducted and recorded according to the current IUF World Record Guidelines.
Competitors will in principle expect that the quality of the results is suitable for world records.

If this is not realistically possible, then the competition results cannot be used for new world records.
In this case, every effort must be made that competitors are made aware of this at least two months in advance.

\section{Ownership of Convention Data}

Each NAUCC or other large unicycling convention is a piece of history.
At the conclusion of NAUCC or other national event, or within one month thereafter, the convention host must supply the USA with all competition and other results, in an agreed digital format (e.g.\ pdf).
This will include all data collected to determine placement and winners at all levels and in all events held at the convention.
This data is considered public, and is not the sole property of the host.

Attendee registration details, judging sheets, protest forms, and related paperwork are not necessarily public.
They are the shared property of the host and the Unicycling Society of America.
On request by the USA Board within a year after closing of NAUCC, the host must make these available to the USA.
Digital data can obviously be copied. Data on paper can either be copied, or the originals can be handed to the USA.

If requested, the host and convention officials must also provide further information, not necessarily in writing, about decisions made, methods used, and other details covered in the process of planning and running the convention.
This information can be invaluable to future hosts, and must not be hidden or lost.

\section{Hierarchy of Officials}

These people make the competition events work.
All of the tasks detailed below must be covered for the events to work.
Names must be assigned for all the jobs listed below, to create a hierarchy of authority for the convention.
All officials are expected to work objectively and impartially.

\subsection{General Officials}

\textbf{USA Board Of Directors:} The USA Board represents the interests of the USA on convention requirements, both in the area of competition rules and the necessary spaces and facilities for them, and for any other requirements that go along with putting on an USA convention.
If problems arise in meeting the requirements, the USA Board and Convention Host work together to find solutions or compromises.
The bulk of this should happen during the early planning stages for a convention, when facilities and schedules are being assembled.

\textbf{USA Convention Liaison:} The Liaison is an optional position. They can represent the USA Board when communicating with convention hosts.
The Liaison essentially has the same powers as the USA Board, but must report to the USA Board and take direction from it.

\textbf{Convention Host:} This is a single person, or a collective group, that has made the commitment to host a unicycle convention using USA rules and guidelines.
By agreeing to host an USA convention, they also agree to follow those rules and guidelines wherever possible.
If known problems arise in the arrangement of facilities, schedules and events, the Host and the USA will work together to resolve the problems.
For the most part, the Convention Host is the ultimate authority for what happens, and does not happen, at the convention.
The exception is any USA requirements for convention facilities or contents, and rules for USA competition events.

\textbf{Top Competition Officials:} Each discipline has a set of authority positions which may include Race or Event Director, (Chief) Referee, Artistic Director and/or Chief Judge.
They are not autonomous, and must answer to the Convention Host.
For Artistic freestyle, it is highly recommended that none of these jobs be combined, and that there be at least one separate person for each.
For other disciplines, combining these roles may be the easy way to organize those events.


\chapter{Competitor Information}

\section{Personal Responsibility}
All attendees should remember that they are guests of the convention hosts, and ambassadors of our sport to all new riders, visitors from far away, and to people in the hosting town.
Remember that the Host is renting the convention facilities, and attendees are expected to treat them well.
Each rider is responsible for the actions of his or her family and non-riding teammates.
Riders may lose placement in races, risk disqualification from events, or be ejected from the convention if they do not work to minimize disruptions from these people.
The Unicycling Society of America does not support
performance enhancing drugs in sport and strives for clean competition.

\section{Supervision of Minors}
A parent, guardian or other designated person, must supervise all minors.

\section{Knowing The Rules}
Lack of understanding of rules will be at the disadvantage of riders, not officials or the USA.
The USA is also not responsible for any errors that may occur in the translation of rules and information into languages other than those in which they were originally written.

\section{Your Privilege}
Entry in the competition is your privilege, not your right.
You are a guest at the Host's event.
You may be in an unfamiliar country, with different customs that are considered the norm.
The Host and convention officials determine whether certain events, age groups, or policies will be used.
As an attendee, you are obligated to obey all rules and decisions of convention officials and hosts.

\section{Nations Represented}
Riders must represent the country in which they hold citizenship, or in which they are a legal resident.
For example, if a rider is attending school in a different country, and is in that country legally, the rider can represent that country, \textit{or} the rider's home country.

If necessary, citizenship or residence may be established with a passport, driver's license, or legal ID for the country the rider wishes to represent.
Riders on extended vacation, exchange students, and other temporary residents of other countries are not eligible to represent those countries, except in multi-rider events (see below).

Because NAUCC is the North American Championship, a rider representing a non-North American country has additional restrictions.
In order to encourage participation by international riders, non-North American competitors will still be allowed to compete at NAUCC, however they cannot be the North American Champion of any event and cannot displace the award of any North American competitor.
The Host can choose to not give the non-North American rider awards or choose to give them awards alongside North American competitors.
For example if a non-North American rider places second in a NAUCC event, the Host can either award this rider second place or ignore their results.
In either case, the North American rider who placed third would be awarded second place, either alone or as a tie.
The Host's policy for non-North American riders should be announced before the start of NAUCC.

\section{Transgender Riders}
NAUCC is committed to providing an open and safe environment for people of all genders.
A rider may register with the gender (male or female) with which the rider identifies most.

\chapter{Host Information}

\section{Convention Aspect}
All competitions need to make every effort to have equal time for the convention side by involving as many competitors as possible and making the event spectator-friendly for other participants as well as non-unicyclists.
Any of the following are examples to achieve this goal:
\begin{itemize}
  \item Workshops related to the event
  \item Fun competitions based on the event
  \item Instant results for the spectators
  \item Ways for other competitors to be introduced to the event
  \item Entertainment during breaks in the competition (such as half time entertainment)
  \item Schedule of the events posted in multiple places
\end{itemize}

\section{Required Events at NAUCC}
NAUCC should include at least the following events.
Hosts are free to add events, age groups, categories or variations that do not appear here, as long as there is no conflict with the existing rules.
When in doubt contact the USA Board.
\begin{itemize}
  \item Track Racing: 800m, 400m, 100m, One-Foot, Wheel Walk, and IUF Slalom.
  \item Road Racing: at least two races, see specific requirements in Chapter 3 of the IUF Rulebook.
   \item Muni: Cross Country, Uphill, Downhill, Cyclocross; see Chapters 4 and 5 of the IUF Rulebook.
   \item Freestyle: Individual, Pairs, Group, and Club Show.
   \item Flatland and Street.
   \item Trials.
  \item Team Games: Hockey and Basketball.
\end{itemize}

\section{Sponsors}

The convention host has the option to seek and obtain private sector sponsorship; for example The Unicycle.com Freestyle Awards, the Coca-Cola Hockey Cup, etc.
This will allow opportunities for external funding to defray costs for host organizations and competitors.
Sponsors are limited to organizations that would not bring the USA into disrepute and are consistent with the aims and objectives of the Unicycling Society of America, Inc.

\section{Materials \& Equipment}
The Host must supply all necessary materials and equipment to run the competitions, such as a timing system, starting posts, cones for the IUF Slalom, etc.
Other materials such as paper and writing materials, judging tables, printers, basketballs, hockey sticks, etc.\ are also necessary.

\section{Early Announcement of Rule Changes}
For all competitions, written rules are needed for any planned events not described in the USA Rulebook, and for events where additional rules are required.
These special rules could be variations on the optional events found in this Rulebook.
Such rules should be published at the same time as registration forms, or earlier, and must be published at least one month before the start of the event.
These rules can be published along with registration forms, and/or on the convention web site.
Competitors need to know the specific rules so they can train for those specific events!
Hosts also need to decide on rules early, so there is less to worry about near competition time.
Rule changes may be a necessary reality, for reasons such as changes in venue, weather or available equipment.
When this happens these changes must be posted to the convention web site immediately.
Examples: Dismount rules or timing details for off-track races, obstacle information for Street Comp, planned age divisions or combination awards.

If competition events or games not found in the USA Rulebook are planned, written rules must be provided.
These rules, if not pre-existing, should be published at the time of announcement of those events.
This generally means at or before the posting of registration forms.
For competitors to properly train, and be on an equal footing with local riders, all must be aware of the rules to be used.

\section{Registration Forms and Waiver}
Because of the various options available to riders in different events, riders may enter different events in different age groups.
A properly structured registration form is essential for making these choices clear to the participants.
For example, a rider may enter Pairs as an Expert with an older rider, but may wish to compete in Individual Freestyle in his or her own age group.
Before publishing, a NAUCC registration form and waiver absolving the USA board and its members from liability should be examined and approved by members of the USA Board of Directors.
No rider may enter any event until his or her registration form has been completed, including payment and completion of waivers and/or signatures.
No minor may compete until a parent or legal guardian has signed his or her release.

\subsection{Combining Age Groups \label{subsec:general_host's-option-unicon_combining-age-groups}}

Later in the registration period or after registration closes, final age groups will be created based on the initial age groups.
This is done by combining initial age groups where needed, as follows:

In a competition with more than 50 riders, six riders are needed to complete an age group.
In competitions with less than 50 riders, six in each age group are still highly recommended, however three riders are the minimum to complete an age group.
Riders generally enter all events with their age group except for events similar to artistic competitions where there are Junior Expert and Expert categories.

The convention host must combine age groups with less than six riders (three riders for smaller conventions) if needed.
This means that initial age groups are not guaranteed.
The combining process can be done on a per-event (per-discipline) basis.

When combining, combine the smallest age group (that is, the age group with the smallest number of participants) with its smallest neighboring age group (either up or down).
If more than one age group is the smallest, choose the age group with the smallest neighbor for combining.
Continue this process until all resulting age groups (combined and/or original) have at least the minimum required/recommended number of participants.
Male age groups and female age groups are never combined.

In exceptional cases it may be decided to split initial age groups.

The final (combined) age groups for all competitions must be published at the latest seven days before the first day of the convention.
Once published, age groups will not change even if competitors drop their events.

\section{Awards}

Because awards are paid for out of the convention budget, and are one of the major expenses of large competitions, the type, number, and quality of awards are the choice of the convention host.
However, these awards must abide to these stipulations:
\begin{itemize}
\item Male and female competitors must be awarded equitably
\item Different Class competitors must be awarded equitably within the same competition (i.e.\ 10k Standard and 10k Unlimited)
\item Awards should be equal within the ranks of Teams, Age Groups, and Champions (i.e.\ 13-14 in Track must be awarded equitably to 16-17 Muni Cross Country)
\end{itemize}

Also all awards must include both the year of the event and one or more of the following:
\begin{itemize}
\item Unicycling Society of America logo
\item The words ``Unicycling Society of America''
\item The words ``North American Unicycling Championships and Convention'' or ``NAUCC''
 \end{itemize}

 The host may determine the amount and level of those awards based upon USA Board approval.
 Generally there are trophies/expert medals for ``top'' events, medals for ``subtop'' events, and ribbons for lower events or places.
 The USA has most usually awarded 1st-3rd place in most events, but this too is up to the convention host.
Once the competition has finished, a personal certificate must be made available to each competitor with a summary of their complete results.
This can be done as an online download, and/or sent through e-mail, and/or made available as a physical copy on the event itself.
The design of the certificates is up to the convention host.

\section{Safety Equipment}

Safety equipment worn by riders must meet the definitions for each, which are found in chapter \ref{chap:general_definitions}.
Hosts may only deviate from these rules for safety equipment if this is inevitable.
The status of ``inevitable'' has to be documented and must be approved by the USA Executive board.
Any deviation from the safety equipment requirements must be approved and announced at least two months before the event.
Additional inevitable changes that arise just before or during an event cannot be approved by the event director alone.
The approval of two USA representatives is required in addition to the event director's approval.
These changes are once again only allowed in the case of the inevitable, and not, for example, due to the wishes of the competitors or judges.

\section{Protests}
An official protest/correction form must be available to riders at all times.
All protests against any results must be submitted in writing on the proper form within two hours after the results are posted, unless there is a shorter time specified for certain events (for example: track racing).
The form must be filled in completely.
This time may be extended for riders who have to be in other races/events during that time period.
Every effort will be made for all protests to be handled within 30 minutes from the time they are received.
Mistakes in paperwork and interference from other riders or other sources are all grounds for protests.
Protests handed in after awards have been delivered will not be considered if the results have been posted for at least three hours before the awards.
If awards are delivered before results are posted, it is recommended to announce the schedule of posting and the deadline for protests at the awarding ceremonies.
All Chief Judge or Referee decisions are final, and cannot be protested.

The host may decide to make official video of some competitions, for example at the start line and/or the finish line, or the 5-meter-line in case of the 50~m one-foot race.
This must be announced before the competition to let the competitors know about their option to protest through this video.

Regardless of whether official video is available, all possible sources of evidence are generally allowed as a means of verification in case of a protest, including (but not limited to) private photos/videos and eyewitness reports.
If someone submits a protest and has evidence that he wants to be considered, he must state that with his protest.
If possible, it is recommended that digital material is copied onto an `official' computer for analysis.
As an alternative, the evidence must be readily accessible, e.g.\ through a contact person and phone number.

In case of video evidence (regardless of its origin), a referee without good skills in video analysis should ask for a skilled assistant in order to prevent incorrect interpretations.

The referee decides which evidence he will consider, and the `value' he assigns to the various pieces of information.
Generally, official camera footage and judge reports will have higher `value' than private evidence.
The objective is that all riders will be judged as fairly as possible.

\section{Open Practice Area}
At least one area with a smooth safe riding surface, sheltered from the weather, should be made available for all or part of the day on most or all days of the convention.
These areas are to be used for non-competition events such as workshops, skills exchange and free practice.

\section{Program Book}

For NAUCC, all registrants shall be provided with an electronic resource containing a full schedule of all events, maps and directions to all event locations, and as much rule and background information as possible.
This information shall be provided by that date that NAUCC commences.
Upon request, a printed schedule will be provided at registration.

\section{Availability of Rulebook}
The host must make sure there are plenty of copies of the rulebook for officials to study on the spot.

\section{Photography and Videography}
The following rules are required for Unicon and are highly recommended for other large international competitions.

In events with closed perimeters, it may be necessary to limit the number of photographers and filmers (hereafter called ``shooters'') allowed inside.
We want great documentation of the events, but not at the expense of safety, and of spectators' ability to see as well.

The following guidelines apply:
\begin{itemize}
\item Shooters must either register ahead of time to be inside the perimeter of an event, or have actual press credentials (professional photojournalists, TV news people, etc.).
\item Registered shooters must have some form of ID given to them, whether it be a pass on a lanyard, a volunteer shirt, or something else to help identify them.
\item The Referee or Head Official for the event has the final say on shooting that can affect the riders and/or spectators' view.
\item The Referee or Head Official should appoint a Media Manager to manage this task.
\item If a Media Manager is used, that person is still under the authority of the Referee or Head Official of the competition.
\item Media Managers must have a good understanding of the needs of shooters to get the job done.
\item Shooters must follow the instructions of the Media Manager or Referee/Head Official, and of the officials at the location.
\item Shooters must generally stay aware at all times of the movements around them.
\item If shooters continue to get in the way and/or not follow instructions they are to be ejected from the perimeter.
\item It is greatly appreciated, but not required, that the shooter submits his or her top shots to the Media Manager during or directly following the convention to be used for the press.
\item Flash is never allowed unless specific permission is given by the event director.
\end{itemize}

\section{Publication of Convention Information}

Convention dates and other information must be announced and/or published at the earliest possible date.
The best way to control the publication of convention information is with a convention web site, with regular updates to provide all the latest information.
For USA and other large events, registration forms should be made available no less than four months before the convention start date.
A list of all planned competition events, including all rules and information pertinent to quality training, should be published at the same time with newly available data to be added as soon as it is known.
Wherever possible, hosts should provide maps, directions and other information to help make people's convention as enjoyable as possible.

\section{Publishing Results \label{sec:publishing_results}}
Results of national and international championships must be published including details such as time, distance, and total score.
For each event, the names and represented nationality of competitors as well as the names and nationality of all officials shall be published.

\section{Option to Remove People From Events}
The host is allowed to remove an individual or a group if they are acting aggressively or abusively against others.
These individuals/groups should be given a first warning, followed by removal from the specific event by the Host or the Chief Judge/Referee who is in charge for the competition where the problem appears.
The person(s) should only be removed from that competition to have a chance to calm down.
If the aggressive or abusive behavior continues, it is also possible to remove the individual or group from the rest of the convention.

\section{USA Public Meeting}

The NAUCC host will provide time in the convention schedule for the USA Public Meeting.
At this meeting, the USA will elect officers or other volunteers, and otherwise do business and encourage the opinions and assistance of all interested convention attendees.

A minimum of one hour should be allocated, during which no other official convention events, other than open gym or other informal activities, should take place.

A meeting room must be provided that has adequate space/seating, lighting and acoustical properties to communicate and conduct the meeting.
A lecture hall or theater are optimal locations, and a sound and/or projection system would be very helpful.

Other USA meetings may be held during the convention, both public and private, but the strict requirements apply only to the big public meeting.

\section{Changes and Cancellations}

The host reserves the right to make changes, if necessary, to ensure the success of a convention or competition.
Sometimes these changes must be made at the last minute, such as in switching outdoor events for indoor in the event of rain.
Sometimes activities must be cancelled due to events beyond the host's control, such as weather or power outages.
When changes or cancellations are made, notification must be posted, communicated and/or distributed as early as possible.

\section{Terminology}
Event hosts must learn and use the proper names and terminology for our sport and competition events.
They should take care not to continue the misuse of outdated or incorrect names and terminology.
The correct ones must be used in all announcements, advertising, publicizing, internal and external documents, and especially in any official documents, such as those within, and printed out by, convention software.

\section{Definitions \label{chap:general_definitions}}

\textbf{Age:} Rider's age for all age categories is determined by their age on the first day of the convention, regardless of whether any events occur that day.
Time of birth, time zones and date of arrival at the convention are not relevant.

\textbf{Coasting:} Unless stated differently, coasting is riding without touching pedals, cranks or any part of the wheel including the tire.
(Freewheeling on a freewheel unicycle is not coasting.)

\textbf{Expert:} The top category in events that don't have a system to determine Finalists.
When no other limitations are present, riders can choose to compete in this category against the other top riders.
Limitations on this may be if top riders are chosen at previous competitions, such as national events, or if there is a limit on the number of competitors per country.
The category is called Expert, and riders entered in it can be called Experts.
The distinction of Experts over Finalists is that they are not chosen based on competition results at the current convention.

\textbf{Figure:} (noun) 1.~A unicycle feat or skill, such as walking the wheel or riding backward, used to describe skills in the Standard Skill event.
2.~A riding pattern, such as a circle or figure 8.

\textbf{Finalist, Finals:} A Finalist is a person, and ``the Finals'' is the last category or group in any event that has multiple rounds.
For example in Track racing, the top riders from the age groups compete against each other in the Finals of most events.

\textbf{Freewheel:} Mechanism allowing the wheel to rotate while the cranks are stationary.

\textbf{Gearing:} Any mechanism that transfers the rotation speed of crank arms to a different rotation speed of wheel.

\textbf{Gloves:} (For racing) Any glove with thick material covering the palms (Leather is acceptable, thin nylon is not).
Gloves may be fingerless, such as bicycling gloves, provided the palm of the hand is completely covered.
Wrist guards, such as those used with in-line skates, are an acceptable alternative to gloves.

\textbf{Helmet:} Helmets must be of bicycle quality (or stronger), and should meet the prevalent safety standards for bicycle (or unicycle) helmets, such as ASTM, SNELL, CPSC, or whatever prevails in the host country.
Helmets for sports other than cycling or skating are not permitted, unless the Referee makes exceptions.
Helmets are required for some events as described in the Safety section of each chapter.

\textbf{IUF:} International Unicycling Federation.
The IUF sponsors and oversees international competitions such as Unicon, creates rules for international competition, and promotes and provides information on unicycling in general.

\textbf{Junior Expert:} Same as Expert, but open only to riders age 0-14.
Riders in this age range may optionally enter Expert instead, to compete in the highest/hardest category.

\textbf{Knee pads:} Any commercially made, thick version is acceptable, such as those used for basketball and volleyball, or any with hard plastic caps.
Knee pads must cover the entire knee and stay on during the whole length of the competition.
Long pants, bandages or patches are not acceptable substitutes.

\textbf{Muni:} Mountain unicycling, or mountain unicycle.
The previous term for this was UMX.

\textbf{Non-unicycling Skills:} (for Freestyle judging) The riding of any vehicle with two or more wheels on the ground, and any skills not performed on a unicycle.
Any skill with more than one support point on the riding surface, such as standing on the unicycle with it lying on the floor, or hopping while standing on the frame (seat on floor); two contact points with the riding surface (wheel and seat), both carrying part of the rider's weight.
The term also refers to skills such as dance, mime, comedy, juggling, playing music or riding vehicles that do not meet the definitions of unicycles.

\textbf{Prop:} Almost anything other than the unicycle(s) being ridden by competitor(s) in a Freestyle performance.
A unicycle being used for a non-unicycling skill (such as a handstand on it while it's lying down) is a prop at that moment.
A hat that is dropped and picked up from the floor is a prop.
A pogo stick or a tricycle (unless ridden on one wheel) is a prop.

\textbf{Shoes:} Shoes with full uppers are required.
This means the shoe must cover the entire top of the foot.
Sandals or thongs are not acceptable.
Shoelaces must not dangle where they can catch in crank arms.

\textbf{Shin guards:} Any commercially made, thick version is acceptable, such as those used for football or bicycling, or any with hard plastic shell.
Shin guards must cover the shin and stay on during the whole length of the competition.
Long pants, bandages or patches are not acceptable as substitutes.

\textbf{Tire Contact Point:} The center of the contact patch between the tire and the riding surface.
Usually judged by eye.

\textbf{Unicycle:} A Unicycle is a vehicle that has a single rolling contact with the riding surface.
It may have multiple wheels, but it must not be possible to ride the unicycle when more than one wheel touches the ground.
It is driven by pedals and cranks which rotate to power the wheel.
It is powered, balanced and controlled by the rider only, with no additional support devices.
Unless noted otherwise, a unicycle may be fitted with handlebars and/or brake(s).

\textbf{Unicycle, Regular:} A regular unicycle is a unicycle with only one wheel.
The cranks are fixed directly and permanently to the wheel's axle.
(This excludes unicycles with gearing even if in 1:1 ratio, a chain drive and/or a freewheel.)
Unless noted otherwise, there are no wheel size and/or crank arm length limitations.

\textbf{Ultimate wheel:} A special unicycle consisting of only a wheel and pedals, with no frame or seat.

\textbf{UMX:} Unicycle Motocross.
This term has been replaced by muni.

\textbf{Unicycling skill:} (noun, for Freestyle judging) Also known as `figure.' Any skills (feats of balance) performed on a vehicle with one support point in contact with the riding surface, this being a wheel, the movement of which is controlled by the rider, thus maintaining balance.
All mounts are also `unicycling skills.'

\textbf{Unintentional dismount:} In most cases, any part of a rider unintentionally touching the ground.
A pedal and foot touching the ground in a sharp turn is not a dismount as long as the foot stays on the pedal while the pedal is on the ground.
Dismounts during many races disqualify the rider.

\textbf{USA:} Unicycling Society of America, Inc.
The USA sponsors and oversees national competitions such as NAUCC, creates rules for national competition, and promotes and provides information on unicycling in general.

\textbf{Unicon:} Unicycling Convention.
This word refers to the IUF World Unicycling Championships.

\textbf{Wheel walking:} Propelling the unicycle by pushing the top of the tire with one or both feet.
Feet touch wheel only, not pedals or crank arms.
A non-pushing foot may rest on the fork.
