\part{Amendments}
\parttoc
\singlechapter{Amendments}

The numbers below refer to sections in the current IUF Rulebook, which at the time of publication, is the ``2017 IUF Rulebook (draft)'' from March 2017. For the sake of clarity, both the number and the name of the referenced IUF Rulebook section will be written below. These amendments replace section 4D.6 and subsection 7B.6.1 of the 2017 IUF Rulebook in their entirety.

\section{IUF Requirements for Continental Championships}
Throughout the IUF Rulebook there are various additional specifications, rules, and requirements for Continental Championships.
This amendment document recognizes that while NAUCC is the Championship event for the North American Continent, these additional stipulations were generally written with much larger Continental Championships in mind.
As such, all additional specifications, rules, and requirements for Continental Championships listed in the IUF Rulebook are treated simply as recommendations for NAUCC.

\amend{4D.6 Ungeared Awards}{Ungeared Champion}
At NAUCC, for each gender (male and female) where there are five or more geared riders in an Unlimited event, the fastest ungeared rider from that gender will be awarded with the North American Ungeared Champion title for that event.
The next two ungeared riders from each gender should also be recognized with an award for second and third place, respectively, in that event.
This is only for the expert classification, not for Age Groups.

\amend{7B.6.1 Group Freestyle Restrictions}{Group Freestyle}
Group freestyle is divided into two categories: Club and Group.
Each rider may enter each category (Club and Group) only once.
For example: a rider can be in a Club routine and a Group routine, but not two Group Routines.

A rider may appear in a second Group Freestyle performance with permission of the Chief Judge, to replace a rider due to illness, injury or other mishap.

\subsection{Group}
Minimum of three riders.

\subsection{Club}
Minimum of three riders. Must be a USA Affiliated Club, and all riders must be members of said club.

\subsection{Minimum Age Groups}
None.

\subsection{Time Limit}
Five minutes for Club, three minutes for Group.

\subsection{Unicycles}
Any type and any number.

\subsection{Music and Costume}
Same as Individual Freestyle.

\subsection{Props and Decoration}
Same as Individual Freestyle.

\subsection{Judging Method}
Same as Individual Freestyle, but with additional emphasis on teamwork and multiple person skills, such as formation riding.
Extra consideration will be given to account for widely different group sizes, relative skill levels, and relative ages of riders.
